---
title: "Danielle Lab 7"
author: "Danielle Poole"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Dani's changes
```{r, include = FALSE} 
library(tidyverse)
gc_df <-read_csv("gc_df.csv")
```
JKM Changes

We are asking: Is there a significant difference in recommended gun control 
action for male and female respondents (should guns be easier, harder, or 
the same difficulty to get)?

Data wrangling and counts

```{r}
# Dani did this. Not JKM.

get_guns <- gc_df %>%
  filter(gender != "NA", make_get_guns != "NA") %>%
  count(gender, make_get_guns) %>%
  spread(make_get_guns, n)%>%
  select(-gender)

rownames(get_guns) <-c("Female", "Male")

get_guns
```

Hi! My name is JKM the collaborator! Here goes our chi-square test for independence!

We ask: "Is there a significant association between sex and opinion on whether guns should be more difficult, easier, or the same difficulty to get?"

```{r}
### Chi-square test for independence (what are proportions?)

# First, let's look at the actual proportions

guns_prop <- prop.table(as.matrix(get_guns), 1)
guns_prop

# Run chi-square test for independence from contingency table

guns_x2 <- chisq.test(get_guns)
guns_x2

# H0: No significant difference

```

"Recommended government action on gun access differed significantly between male (n = ) and female (n = ) respondents ($\chi^2$(`r guns_x2$parameter`) = ..... p < 0.001. Notably, a much higher proportioin of female respondents (57.4%) recommend making it more difficult to get guns, compared to 40.4% of male respondents."







